MLH1 data report 

### 2017-11-03 rmd_report.rmd
added batch color to indiviual mouse distributions

for(i in 1:(length(df_list))){
 # print(i)
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
 # print(sub_mouse_means)
  #below should work -- I think I need to go througheach row of the df_list[[i]]
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}
#remove CAST, this column isn't added to MLH1 col, it's added to df_list
#The above adds a column of mouse specific averages to a giant list of dataframes. Each dataframe in the list is specific to a category.
#the next step is to make plots from this giant list of dataframes
# I can delete all of the code below that by hand makes

### not make a loop for ggplot... or giant ggplot base that uses latice smartly
# make new ggplots -- that are replaces

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf + geom_point(stat = "identity")+ geom_jitter()
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red")
  plot_list[[h]] =   pf
}

#aes must be same length --- 
# the last one is correct....?

>>>>

for(i in 1:(length(df_list))){
 # print(i)
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
 # print(sub_mouse_means)
  #below should work -- I think I need to go througheach row of the df_list[[i]]
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red")
  plot_list[[h]] =   pf
}

#aes must be same length ---   #geom_point(stat = "identity") +
# the last one is correct....?
